\section{Introduction}

"Data is the new oil, and databases are the engines that refine it". In today's competitive retail world, firms must manage both their physical and online operations efficiently to fulfill customer expectations and maximize resources. The design of a full database is important to ease the integration of inventory, sales, and customer information, and provide connection operations between both channels. This report portrays the architecture of a database for a retail business that operates in both physical and online modes, represented through an Entity-Relationship (ER) diagram.

The main goal of this database is to offer flawless coordination across the store's physical inventory and its online site. The ER diagram highlights the connection between significant entities such as Customers, Products, Orders, and Employees demonstrating how data interacts within the system. It acts as the core of the database that maintains efficient retail processes, ensuring correctness, consistency, and scalability.

This report represents NexStore company's main database design using an Entity-Relationship diagram. The References section contains all the used citations. The Tools section describes all the instruments used to draw database design. The System Description and Requirements section defines all the needs of the client. The Legend of ER diagram symbols include all the symbols of the used notation. The complete ER diagram is presented in the ER diagram for the NexStore database section. In the subsection "Entity Types \& Their Attributes", we elucidate the various types and attributes of each entity. In the other subsection "Relationships and Their Explanations", all relationships are listed and explained. In the "Conclusion" section, we summarize the main points of the design document.
