
\section{System Description \& Requirements}

\begin{enumerate}
  \item Supplier is identified by supplier's name, contact information including email, name and phone number, and website.
  \item Product is identified by SKU, price, name, description, and image URLs that might include several images, colors, weights, brands, and dimensions (width, height, length).
  \item The category is identified by name and description.
  \item The employee is identified by SSN, hire date, date of birth, gender, address, phone number, email, name, position, and salary.
  \item Address consists of country state, street, building, and apartment.
  \item The branch is identified by phone number, name, address, and work hours (opening hours, closing hours) of the branch which might have different values depending on the day.
  \item The customer is identified by phone number, date of birth, address, hashed password to ensure security, date of registration, email, name, and gender.
  \item Order is identified by order ID, notes, payment method, total amount, and whether the order is online.
  \item The department is identified by name, locations (it might have several locations), and an updated number of employees.
  \item Driver is identified by license number, driving experience years, and license expiry date.
  \item The coupon is identified by code, discount percentage, number of times used, minimum and maximum order amount, usage limit, description, and time interval of validation (valid to, valid from).
  \item Suppliers could supply zero or more products, and every product should be supplied by exactly one supplier.
  \item Every product should be listed under exactly one category, which might be a subcategory of exactly one parent category.
  \item An order must contain at least one product, and a product could be contained in several orders.
  \item The relationship between the product and the order takes the quantity and the amount -in USD- of the product as attributes.
  \item Every order is made by exactly one customer; however, a customer could have several orders.
  \item The relationship between the customer and the order takes the date of when the order was processed.
  \item Every product must be in at least one branch, but a branch could have many products.
  \item The relationship between the products and branches takes the quantity of the product and on which shelf it is placed as attributes.
  \item A customer might review many products, and a product could be reviewed by several customers.
  \item Reviews relationship takes the review date, rating, and image URLs that might have several images, comments, and descriptions as attributes.
  \item Every employee should work in exactly one branch, and a branch should have one or many employees.
  \item Every employee should be supervised by exactly one other employee, and an employee could supervise many employees.
  \item Every branch should be managed by exactly one employee, and an employee might manage a branch.
  \item An order must be physically checked out by exactly one employee, and an employee could physically check out many orders.
  \item Every department should have at least one employee, and each employee should work for exactly one department.
  \item All relationships between the departments and the employees include the date when the employee started working for the department as an attribute.
  \item Every department should be managed by exactly one employee, but an employee could manage a department.
  \item An employee might have some dependents, but a dependent must depend on exactly one employee.
  \item Dependent is identified by name, gender, date of birth, and his/her relationship to the employee.
  \item A driver is an employee, but not every employee is a driver.
  \item Every order should be delivered by exactly one driver, but a driver could deliver several orders.
  \item The relationship between the driver and the order takes the address, and actual and expected time of delivery as attributes.
  \item An order could be redeemed by one coupon, and a coupon could be redeemed by one order.
  \item The relationship between the order and the coupon takes the redemption date and discount amount -in USD- as attributes.
  \item The relationship wishlist must be requested by a customer and could be empty or could include several products.
  \item Wishlist takes as an attribute the total amount of the products.
  \item The relationship between the customer and the support ticket takes the requested date as an attribute.
  \item The support ticket is identified by ticket number, description, subject, status, and priority.
  \item Every support ticket should be assigned to exactly one employee, but an employee could be assigned to many support tickets.
  \item The relationship between the employee and the support ticket takes the assignment date as an attribute.
\end{enumerate}
