\section{Conclusion}

In this project, we have structured a database design for a retail shop, supporting an organized solution for tracking products, customers, suppliers, and orders. Through this system, we showed the capability of this system to capture core business operations such as monitoring product availability, maintaining supplier relationships, and storing customer orders. The project also sheds light on the significance of data normalization to minimize redundancy and implement relationships to properly capture business logic.

All in all, the project acts as a solid basis for the retail shops' futuristic scalability operations with the capability of designing additional functionalities like data analysis, finance, and e-commerce integration. The skills acquired while developing the database expanded our understanding of the main fundamental principles and pillars of database design, which will reflect effectively on our future real-world applications.

In designing the relations and selecting foreign keys, we ensured that the database structure accurately reflects the relationships between different entities, such as products, customers, orders, and suppliers. Each relation was carefully created with primary keys to uniquely identify records, and foreign keys were used to link related tables, ensuring data integrity across the system. This design not only prevents redundancy but also ensures that changes made in one table (like updating a customer's information) are reflected wherever relevant. By establishing these relationships through foreign keys, we maintain consistency and reliability in the database, laying a strong foundation for seamless data management and scalability.

In the next phase, we will implement the database design using SQL in PostgreSQL, turning our plan into a working system that supports real business operations. This step involves creating tables, setting relationships, and writing SQL queries to manage data efficiently. We'll also explore features like triggers and views to automate tasks, ensuring data stays consistent and organized. Additionally, we'll focus on performance optimization with indexing, as well as managing user roles and security to protect sensitive information. This practical phase will help us gain hands-on experience with SQL, solidify our understanding of database management, and prepare us for real-world applications.
